Using a Two-Layer Neural Network and Physicochemical Properties to Classify Glass for Forensic Analysis

### 2017-06-25 Paper/paper.tex
Paper Editing and Formatting

\author{%
\name{Michael Arango, Mark Barna \& Paul Brewster}}

%\abstract{abstract text goes here...}
\date{\today}
\maketitle

@@

The dataset we chose for analysis was made available for download from the UCI Machine Learning Repository and was created by the USA Forensic Science Service. There are 214 observations of 9 different features along with 214 targets that specify whether the glass sample came from a window or not. While we would like more data to train a neural network, we believe the dataset is large enough for our purposes. It is difficult to know before we train a neural network if we have enough data, but the amount of data required is directly related to the complexity of the underlying decision boundary we are trying to implement. We won't 
know how complex the decision boundary we are trying to approximate is until we train the network, but we feel confident using the dataset as many others have used the dataset and found robust results. Several others papers in the literature use much more complex methods than we will employ and have not found the size of the data to be an issue.

@@

\section{Literature Review}
\label{sec2}

\section{Preparing your manuscript}
\label{sec3}

@@

\begin{enumerate}
\item
\LaTeX\ and \AmS-\LaTeX\ provide a rich set of commands for all common, important
features of your paper. Use them; avoid definitions and use of custom commands.

\item
There is no need to redefine any \TeX, \LaTeX\ or \AmS-\LaTeX\ commands.

\item
Avoid direct formatting for headings cleanly set as section headings.

\item
Use \LaTeX\ commands for font changes. For example: use \verb+\textbf{phrase}+,
not \verb+{\bf phrase}+; use \verb+\mathcal{C}+, not \verb+{\cal C}+; etc.
\end{enumerate}

\subsection{How to start with \texttt{ouparticle.cls}}
\label{sec3.2}

Before you type anything that actually appears in the paper, you need to
include a \verb+\documentclass{ouparticle}+ command at the very beginning,
and then the two commands that have to be part of any \LaTeX\ document,
\verb+\begin{document}+ at the start and \verb+\end{document}+ at the
end of your paper.

\subsection{Document structure}
\label{sec3.3}

The main structure of your paper is as follows:

\begin{verbatim}
\documentclass[12pt,...]{ouparticle}
\usepackage[...]{packages}

\title{...}
\author{
    \name{...}
    \address{...}
    \email{...}
        \and
    \name{...}
    \address{...}
    \email{...}
        \and
    \name{...}
    \address{...}
    \email{...}
}
\abstract{...}
\keywords{...}

\maketitle

\section{....}
...
\subsection{....}
....
\end{document}
\end{verbatim}

\subsection{Options}
\label{sec3.4}

@@

\begin{description}
\item \textbf{oneline:}
This option will set your entire manuscript in one line spacing.
It will not affect the footnote, figure and table environments.

\item \textbf{halfline:}
This is to set your entire manuscript in half line spacing.

@@

\item \textbf{nonumbib:} For unnumbered bibliography.
\end{description}

\subsection{Front matter}
\label{sec3.5}

The title of the manuscript is simply specified by using the \verb+\title{text}+ command in
the same manner as in this sample. Author's information consists of the name of the author
and the corresponding institutions with addresses, as given in this example. Include an
electronic mail address if available, inserting it into the \verb+\email{text}+ commands.
You may follow the same coding if there are more than one author; separate authors with
\verb+\and+. Please identify the corresponding author with his/her electronic
mail address by \verb+\thanks{text}+. An abstract for your paper is specified by using
\verb+\abstract{text}+. A \verb+\keywords{text}+ macro may also be used to indicate keywords for the
article. Use \verb+\maketitle+ after the abstract and keywords to make the header of your article.

@@

To begin a new section, give the heading of that section in the \verb+\section{text}+ command.
A section number is supplied automatically. Use the starred form (\verb+\section*{text}+) of the
command to suppress the automatic numbering. If you want to be able to make reference to that section,
then you need to \texttt{label} it (see Section \ref{sec3.14}). You can have sections up to
five levels. The sectioning commands are \verb|\section|, \verb|\subsection|, \verb|\subsubsection|,
\verb|\paragraph| and \verb|\subparagraph|.

\subsection{Ordinary text}
\label{sec3.7}

The ends of words and sentences are marked by spaces. It does not matter how many
spaces you type. The end of a line counts as a space. One
or more blank lines denote the end of a paragraph.

There are a number of things for which you need to follow different
methods. As you know, quotation marks, quotes within quotes,
dashes, ellipsis, etc. should be as per the \LaTeX\ standard input. \LaTeX\ interprets some
common characters as commands, and therefore you must instead type those common characters as
specific \LaTeX\ commands to generate them. Those characters are \$, \&, \%, \#, \{, and \}.

\subsection{Formatting}
\label{sec3.8}

One should always use \LaTeX\ macros rather than the lower-level
\TeX\ macros like \verb+\it+, \verb+\bf+ and \verb+\tt+. The
\LaTeX\ macros offer much improved features. The following table summarizes the font
selection commands in \LaTeX.

@@

Use normal \LaTeX\ coding for figures and tables.
Figure and table environments should be inserted after (not in) the paragraph in which
the figure is first mentioned or grouped all
together at the end of the file. They will be numbered automatically.
The following is an example of typesetting a table.

@@

Equations are used in the same way as described in the \LaTeX\ manual.
Do not start a paragraph with a displayed equation. Equations are numbered consecutively, with equation numbers
in parentheses flush right.
 For example, if you type
\begin{verbatim}
\begin{equation}\label{eq1}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]
\int^{\infty}_0\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0
(\lambda r_i\,\lambda {\rm d}\lambda)
\end{equation}
\end{verbatim}
then you will get the following output:
\begin{equation}\label{eq1}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]\int^{\infty}_0
\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0 (\lambda r_i\,\lambda {\rm d}\lambda)
\end{equation}
It inserts space both above and below the equation. \AmS-\LaTeX{} has several environments that
make it easier to typeset complicated multiline displayed equations. These are explained in the
\AmS-\LaTeX{} User Guide. A \verb+subequation+ environment is available to create equations with
sub-numbering of the equation counter. It takes one (optional)
argument to specify the way that the sub-counter should appear.

\subsection{Displayed text}
\label{sec3.11}

Text is displayed by indenting it from the left and right margins.
Quotations are commonly displayed. There are short
quotations:
\begin{quote}
   This is a short quotation.  It consists of a
   single paragraph of text.  See how it is formatted.
\end{quote}
and longer ones:
\begin{quotation}
   This is a longer quotation.  It consists of two
   paragraphs of text, neither of which are
   particularly interesting.

   This is the second paragraph of the quotation.  It
   is just as dull as the first paragraph.
\end{quotation}
You can even display poetry.
\begin{verse}
   There is an environment
    for verse \\             % The \\ command separates lines
   Whose features some poets % within a stanza.
   will curse.

                             % One or more blank lines separate stanzas.

   For instead of making\\
   Them do \emph{all} line breaking, \\
   It allows them to put too many words on a line when they'd rather be
   forced to be terse.
\end{verse}

@@

\subsection{Displayed sentences: theorems and such}
\label{sec3.13}

These environments have to be defined with the help of \LaTeX's \verb+\newtheorem+ command, and
also with the \AmS-\LaTeX\ package for theorems that is already with your class file.
For example, \verb+\newtheorem{thm}{Theorem}+. Predefined theorem styles can be used in your article
to differentiate the theorem-like environments. You can have an extra command, \verb+\newproof+,
that can be used for displayed text. The following is an example of using the above-defined
\verb+thm+ environment.
\begin{verbatim}
\begin{thm}
This is body matter for this environment.
\end{thm}
\end{verbatim}

\subsection{Cross-referencing}
\label{sec3.14}

\LaTeX\ possesses features for labelling and cross-referencing
section headings, equations, tables, figures and theorems.
Their proper usage in the context of section headings, equations,
tables and figures are discussed in the appropriate sections.

Cross-referencing depends upon the use of `keys' that are defined by the user.
The \verb+\label{key}+ command is used to identify the links. Keys are strings of
characters that serve to label section headings, equations, tables and figures
that replace explicit, by-hand numbering. The \verb+\ref{key}+ command is used for
cross-referencing.

Files that use cross-referencing (and almost all manuscripts do)
need to be processed through \LaTeX\ at least twice to
ensure that the keys have been properly linked to the appropriate numbers.

\subsection{Footnotes and endnotes}
\label{sec3.15}

The footnote text can either appear at the bottom of a page or at the end of your paper.
The \verb+\footnote+ macro \emph{should not} be used in the front matter to provide additional
information about authors (such as corresponding addresses); instead, use \verb+\thanks{text}+ commands.
The document option `\texttt{endnotes}' is used to make endnotes. The command \verb+\theendnotes+ should
be used to place the endnotes at the required location in the text. They will be put in a separate
`Notes' section.

\subsection{Appendix}
\label{sec3.16}

The \verb+\appendix+ command signals that all following sections are
appendices, and therefore the headings after \verb+\appendix+ will be set
as appendix headings. For a single appendix, use \verb+\appendix*+ followed by the \verb+\section{text}+
command to suppress the appendix letter in the section heading.

\subsection{Special sections for notes and acknowledgements}
\label{sec3.17}

If you wish to include a `Notes' or `Acknowledgements' section in your paper,
use the \verb+\begin{notes}...\end{notes}+ macro. We use the same environment for both
`Notes' and `Acknowledgements'. The following examples show to how to use this macro.
\begin{verbatim}
\begin{notes}
Please note that this class file is provided as it is, and
copyright by Oxford University Press. You are free to use this
class file, provided that you do not make changes in this class file.
If you do make changes, you are requested to rename the class file.
\end{notes}

\begin{notes}[Acknowledgements]
The authors would like to thank...
\end{notes}

\end{verbatim}

\subsection{References}
\label{sec3.18}

The reference entries can be \LaTeX\ typed bibliographies or generated through a BIB\TeX\ database.
BIB\TeX\ is an adjunct to \LaTeX\ that aids in the preparation of bibliographies. BIB\TeX\
allows authors to build up a database or collection of bibliography entries that may be used for many
manuscripts. They also save us the trouble of having to specify formatting. More details can be found
in the \textit{BIB\TeX\ Guide}. For \LaTeX\ reference entries use the
\verb+\begin{thebibliography}....\end{thebibliography}+ environment (see below) to make references in your paper.
We have provided the class file option to distinguish two styles of references. Those options are \verb+numbib+ and \verb+nonumbib+.
You can select one of these options with the \verb+\documentclass+ command. By default the class file will take the
\verb+numbib+ option. The following is an example of \LaTeX\ bibliography.

\begin{verbatim}
\begin{thebibliography}{0}
\bibitem{bib1}
Goossens, M., F. Mittelbach, and A. Samarin: {\em The {\LaTeX} Companion}.
Addison-Wesley, Reading, MA, USA, 1994.
\bibitem{bib2}
Knuth, D.E: {\em The {\TeX}book}. Addison-Wesley, Reading, MA, USA, 1984.
\bibitem{bib3}
Lamport, L.: {\em {\LaTeX} -- A Document Preparation System -- User's
Guide and Reference Manual}. Addison-Wesley, Reading, MA, USA, 1985.
\bibitem{bib4}
Smith, I.N., R.S. Johnes, and W.P. Hines: 1992, `Title of the Article',
\textit{Journal Title in Italics} \textbf{Vol. no. X}, pp. 00--00
\end{thebibliography}
\end{verbatim}

\section{Macro packages}
\label{sec4}

The following packages are compulsorily needed by the class file:
\begin{verbatim}
amsmath         graphicx
amssymb         endnotes
amsfonts        setspace
verbatim        geometry
\end{verbatim}

The commonly used packages already used by this class file that authors can use whenever required are:
\begin{verbatim}
xspace          latexsym        url
amscd           multicol        algorithm
rotating        array           subfigure
\end{verbatim}

Additionally, you can use other packages and these should be loaded
using the \verb+\usepackage+ command.

>>>>

\author{%
\name{Michael Arango}
\email{mikearango@gwu.edu}
	\and
\name{Mark Barna}
\email{mark.barna@gmail.com}
	\and
\name{Paul Brewster}
\email{pfbrewster@gmail.com}
}

%\abstract{abstract text goes here...}
\date{\today}
\maketitle
\pagebreak
\tableofcontents
\pagebreak

@@

The dataset we chose for analysis was made available for download from the UCI Machine Learning Repository and was created by the USA Forensic Science Service. There are 214 observations of 9 different features along with 214 targets that specify whether the glass sample came from a window or not. While we would like more data to train a neural network, we believe the dataset is large enough for our purposes. It is difficult to know before we train a neural network if we have enough data, but the amount of data required is directly related to the complexity of the underlying decision boundary we are trying to implement. We won't 
know how complex the decision boundary we are trying to approximate is until we train the network, but we feel confident using the dataset as many others have used the dataset and found robust results. Several other papers in the literature use much more complex methods than we will employ and have not found the size of the data to be an issue.

@@

\section{Introduction}
\label{sec2}
An overview of the project and an outline of the report (I like to write intro after I finish a project).

\subsection{Literature Review}
\label{sec3}

\section{Description of the Dataset}
\subsection{Inputs}
\subsection{Targets}

\section{Description of the Network Architecture and Training Algorithm}

\subsection{Network Architecture}
\subsection{Training Algorith}

\section{Experimental Setup}

\subsection{Data Preprocessing}
\subsection{Implementation of the Network}
\subsection{Performance Index}

\section{Results}

\section{Conclusion}

@@

@@

\begin{description}

@@

\end{description}

@@

 If you want to be able to make reference to that section,
then you need to \texttt{label} it (see Section \ref{sec3.14}).

@@

The following is an example of typesetting a table.

@@

For example, if you type
\begin{verbatim}
\begin{equation}\label{eq1}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]
\int^{\infty}_0\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0
(\lambda r_i\,\lambda {\rm d}\lambda)
\end{equation}
\end{verbatim}
then you will get the following output:
\begin{equation}\label{eq1}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]\int^{\infty}_0
\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0 (\lambda r_i\,\lambda {\rm d}\lambda)
\end{equation}

@@

\pagebreak

\addcontentsline{toc}{section}{References}
\begin{thebibliography}{0}
\bibitem{bib1}
Goossens, M., F. Mittelbach, and A. Samarin: {\em The {\LaTeX} Companion}.
Addison-Wesley, Reading, MA, USA, 1994.
\bibitem{bib2}
Knuth, D.E: {\em The {\TeX}book}. Addison-Wesley, Reading, MA, USA, 1984.
\bibitem{bib3}
Lamport, L.: {\em {\LaTeX} -- A Document Preparation System -- User's
Guide and Reference Manual}. Addison-Wesley, Reading, MA, USA, 1985.
\bibitem{bib4}
Smith, I.N., R.S. Johnes, and W.P. Hines: 1992, `Title of the Article',
\textit{Journal Title in Italics} \textbf{Vol. no. X}, pp. 00--00
\end{thebibliography}

\pagebreak
\appendix

\section{Perceptron}
\section{Backprop}
\section{Subroutine X}
